### 2017-08-28 paper/incomeShocks-jde-r1.tex
Update variable labels and table notes

% Village crop loss

\begin{table}[htbp]
\begin{center}
\begin{small}
\begin{threeparttable}
\caption{The Effects of Individual and Village Crop Loss}
\label{tab:vill_croploss}
\begin{tabular}{@{} l D{.}{.}{1.5} D{.}{.}{1.5}  D{.}{.}{1.5} D{.}{.}{1.5} D{.}{.}{1.5}  @{}}
\toprule
                                                       & \mco{}              &\mco{}               &\multicolumn{3}{c}{Contraceptive Use}\\ \cmidrule(lr){4-6}
                                                       & \mco{Pregnant}      &\mco{Birth}          &\mco{Any}            &\mco{Traditional}    & \mco{Modern}        \\ \midrule
Crop loss - 1-7 months (200 TZS or above)              &      -0.105\sym{**} &                     &       0.071\sym{**} &       0.047\sym{**} &       0.006         \\
                                                       &     (0.049)         &                     &     (0.032)         &     (0.023)         &     (0.021)         \\
Fraction with crop loss in village                     &       0.059         &                     &      -0.003         &       0.030         &      -0.013         \\
                                                       &     (0.108)         &                     &     (0.070)         &     (0.056)         &     (0.039)         \\
Crop loss - 7-14 months (200 TZS or above)             &                     &      -0.152\sym{***}&                     &                     &                     \\
                                                       &                     &     (0.058)         &                     &                     &                     \\
Lagged fraction with crop loss in village              &                     &      -0.033         &                     &                     &                     \\
                                                       &                     &     (0.120)         &                     &                     &                     \\
\addlinespace 
Wave dummies                                           &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Woman fixed effects                                    &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        &    \mco{Yes}        \\
Observations                                           &    \mco{988}        &    \mco{741}        &    \mco{988}        &    \mco{988}        &    \mco{988}        \\
Number of women                                        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        &    \mco{247}        \\
\bottomrule
\end{tabular}
\begin{tablenotes} \footnotesize
\item \hspace*{-0.5em} \textbf{Note.}
Robust standard errors clustered at household level in parentheses; 
* significant at 10\%; ** significant at 5\%; *** significant at 1\%.
Crop loss is a dummy for a per capita crop loss of 200 TZS or above.
Assets are per capita and measured in 10,000 TZS.
\end{tablenotes}
\end{threeparttable}
\end{small}
\end{center}
\end{table}

>>>>

% Village crop loss 
\input{../tables/appendix_village.tex}
